### 2016-05-19 2016-lrec-tyvmorph/poster.tex
moar poster dev
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@68625 72bbbca6-d526-0410-a7d9-f06f51895060

\usepackage{tikz}
\usetikzlibrary{shapes,arrows} %for flowchart
% Define block styles
\newcommand{\flowchartscale}{0.85}
\tikzstyle{decision} = [diamond, draw, fill=iumint, 
    text width=5em, text badly centered, node distance=3cm, inner sep=0pt,
	 font=\diagsans, scale=\flowchartscale]
\tikzstyle{block} = [rectangle, draw, fill=iulimestone, 
    text width=5em, text centered, rounded corners, minimum height=4em,
	 font=\diagsans, scale=\flowchartscale]
\tikzstyle{line} = [draw, -latex', thick, font=\diagsans]
\tikzstyle{cloud} = [draw, ellipse,fill=iumidnight, text=grey, text width=8em,
	text centered, %node distance=3cm,
	minimum height=2em, font=\diagsans, scale=\flowchartscale]
%\usepackage{pgfbaselayers}
%\pgfdeclarelayer{background}
%\pgfdeclarelayer{foreground}
%\pgfsetlayers{background,main,foreground}

@@

		\headerbox{Development cycle}{name=development,below=morphtrans,span=2}{
		\centering
		\begin{tikzpicture}[xscale=3,yscale=2.8]%, auto]

@@

	\headerbox{Example}{name=example,span=2,column=1,row=0}{
	« Бис кожууннуң соңгукчулары-биле ажылды чорутпастай бээривиске, көргүзүглер баксыраан. »\\

		%\texttt{алд\hilitegrey{>}\archiphon{I}м}\hfill{}\hilitetwo{↔}\hfill{}\texttt{алд\tag{n}\tag{px1sg}\tag{nom}}

		\texttt{\textasciicircum Бис/бис\tag{prn}\tag{pers}\tag{p1}\tag{pl}\tag{nom}\$}\\
		\texttt{\textasciicircum кожууннуң/кожуун\tag{n}\tag{gen}\$}\\
		\texttt{\textasciicircum соңгукчулары/соңгукчу\tag{n}\tag{pl}\tag{px3sp}\tag{nom}\$}\\
		\texttt{\textasciicircum -биле/биле\tag{post}\$}\\
		\texttt{\textasciicircum ажылды/ажыл\tag{n}\tag{acc}\$}\\
		\texttt{\textasciicircum чорутпастай/чорут\tag{v}\tag{tv}\tag{cess}\tag{prc\_impf}\$}\\
		\texttt{\textasciicircum бээривиске/бер\tag{vaux}\tag{ger\_aor}\tag{px1pl}\tag{dat}\$}\\
		\texttt{\textasciicircum ,/,\tag{cm}\$}\\
		\texttt{\textasciicircum көргүзүглер/көргүзүг\tag{n}\tag{pl}\tag{nom}\$}\\
		\texttt{\textasciicircum баксыраан/баксыра\tag{v}\tag{iv}\tag{past}\tag{p3}\tag{pl}\$}\\
		\texttt{\textasciicircum ./.\tag{sent}\$}

@@

	\headerbox{Lexicon}{name=lexicon,column=1,below=example}{
		\begin{tabular}{llr}
			\toprule
			Part of speech	&	Tag	& Stems \\
			\midrule
			Noun & \tag{n} & 4,226 \\
			Proper noun & \tag{np} & 4,217 \\
			Adjective & \tag{adj} & 1,603 \\
			Verb & \tag{v} & 1,064 \\
			Adverb & \tag{adv} & 136 \\
			Numeral & \tag{num} & 85 \\
			Conjunction & \tag{cnj*} & 70 \\
			Postposition & \tag{post} & 28 \\
			Pronoun & \tag{prn} & 35 \\
			Determiner & \tag{det} & 26 \\
			\midrule
			Total &  & 11,490 \\
			\bottomrule
		\end{tabular}
	}

	\headerbox{Evaluation}{name=results,column=1,below=lexicon}{

@@

		\headerbox{Ongoing and future work}{name=nedostatki,column=2,below=example}{
		\htwo{our other Turkic-language transducers}
		\begin{itemize}
			%\item Turkish (\hiliteone{Çöltekin, 2010 \& 2014}; \hilitetwo{Oflazer, 1994})
			%\item Crimean Tatar (\hilitetwo{Altıntaş, 2001})
			%\item Turkmen (\hilitetwo{Tantuğ et al., 2006})
			%\item Kazakh (\hilitetwo{Бекманова \& Махимов, 2013})
			%\vspace{1pt}\hfill{} \hiliteone{GPL (=free and open)}!
			%\item our Kyrgyz, Kazakh, Tatar, Kumyk:\ all \hiliteone{GPL (=free and open)}!
			\item \textbf{Kyrgyz} \parencite{jnwmifmt2012lrecpaper}%  (Washington et al., 2012)
			\item \textbf{Tatar} \& \textbf{Bashkort} \parencite{fmtjnwisrb2012lrecpaper} %(Tyers et al., 2012)
			\item \textbf{Kazakh} \parencite{isjnwfmt2013mtsummitpaper} %(Salimzyanov et al., 2013)
			\item \textbf{Kumyk} \parencite{jnwisfmt2014lrecpaper} %(Washington et al., 2014)
			\item ongoing work on Sakha, Khakas, and more!
		\end{itemize}
		\dividerspace{}

@@

	\headerbox{References}{name=references,below=nedostatki,column=2}{
		\vspace{-0.42em}
		\begin{spacing}{0.3}
			\printbibliography[heading=none]
		\end{spacing}
		\vspace{-0.05em}
	}

>>>>

\usepackage{tikz}
\usetikzlibrary{shapes,arrows} %for flowchart
% Define block styles
\newcommand{\flowchartscale}{0.6}
\tikzstyle{decision} = [diamond, draw, fill=iumint, 
    text width=5em, text badly centered, node distance=3cm, inner sep=0pt,
	 font=\diagsans, scale=\flowchartscale]
\tikzstyle{block} = [rectangle, draw, fill=iulimestone, 
    text width=5em, text centered, rounded corners, minimum height=4em,
	 font=\diagsans, scale=\flowchartscale]
\tikzstyle{line} = [draw, -latex', thick, font=\diagsans]
\tikzstyle{cloud} = [draw, ellipse,fill=iumidnight, text=grey, text width=8em,
	text centered, %node distance=3cm,
	minimum height=2em, font=\diagsans, scale=\flowchartscale]
%\usepackage{pgfbaselayers}
%\pgfdeclarelayer{background}
%\pgfdeclarelayer{foreground}
%\pgfsetlayers{background,main,foreground}

@@

		\headerbox{Development cycle}{name=development,below=morphtrans,span=1}{
		\centering
		\begin{tikzpicture}[xscale=1.45,yscale=2.2]%, auto]

@@

	\headerbox{Example}{name=example,span=2,column=1,row=0}{
	{\centering
	{\fontsize{12pt}{12pt}\selectfont \em{« Бис кожууннуң соңгукчулары-биле ажылды чорутпастай бээривиске, көргүзүглер баксыраан. »}}\vspace{0.5em}\\
	{\fontsize{12pt}{12pt}\selectfont ``Figures worsened when we stopped conducting business with the district's constituents.''}\\
	%Когда мы перестали проводить работу с избирателями кожууна, показатели ухудшились
	}
	%\vspace{-1em}

		%\texttt{алд\hilitegrey{>}\archiphon{I}м}\hfill{}\hilitetwo{↔}\hfill{}\texttt{алд\tag{n}\tag{px1sg}\tag{nom}}
	\begin{multicols}{2}
	{\fontsize{14pt}{14pt}\selectfont
		\texttt{\textasciicircum Бис/бис\tag{prn}\tag{pers}\tag{p1}\tag{pl}\tag{nom}\$}\\
		\texttt{\textasciicircum кожууннуң/кожуун\tag{n}\tag{gen}\$}\\
		\texttt{\textasciicircum соңгукчулары/соңгукчу\tag{n}\tag{pl}\tag{px3sp}\tag{nom}\$}\\
		\texttt{\textasciicircum -биле/биле\tag{post}\$}\\
		\texttt{\textasciicircum ажылды/ажыл\tag{n}\tag{acc}\$}\\
		\texttt{\textasciicircum чорутпастай/чорут\tag{v}\tag{tv}\tag{cess}\tag{prc\_impf}\$}\\
		\texttt{\textasciicircum бээривиске/бер\tag{vaux}\tag{ger\_aor}\tag{px1pl}\tag{dat}\$}\\
		\texttt{\textasciicircum ,/,\tag{cm}\$}\\
		\texttt{\textasciicircum көргүзүглер/көргүзүг\tag{n}\tag{pl}\tag{nom}\$}\\
		\texttt{\textasciicircum баксыраан/баксыра\tag{v}\tag{iv}\tag{past}\tag{p3}\tag{pl}\$}\\
		\texttt{\textasciicircum ./.\tag{sent}\$}}\\
		\tikzoverlay[text width=10em] at (3.3in, 0in) {
			Lexicon contents {\qipa ↗}
		};
		\columnbreak

		\hspace*{1in}\begin{tabular}{llr}
			\toprule
			Part of speech	&	Tag	& Stems \\
			\midrule
			Noun & \tag{n} & 4,226 \\
			Proper noun & \tag{np} & 4,217 \\
			Adjective & \tag{adj} & 1,603 \\
			Verb & \tag{v} & 1,064 \\
			Adverb & \tag{adv} & 136 \\
			Numeral & \tag{num} & 85 \\
			Conjunction & \tag{cnj*} & 70 \\
			Postposition & \tag{post} & 28 \\
			Pronoun & \tag{prn} & 35 \\
			Determiner & \tag{det} & 26 \\
			\midrule
			Total &  & 11,490 \\
			\bottomrule
		\end{tabular}\\

	\end{multicols}

@@

	%\headerbox{Lexicon}{name=lexicon,column=1,below=example}{
	%	%\resizebox{0.9\textwidth}{!}{
	%	%}
	%}

	\headerbox{Evaluation}{name=results,column=2,below=example}{ %lexicon}{
		\begin{multicols}{2}	
		\begin{tabular}{lrr}
			\toprule
				& precision & recall \\
			\midrule
			known & 0.99 & 0.97 \\
			all & 0.99 & 0.69 \\
			\bottomrule
		\end{tabular}\\
		{\qipa ↑} quantitative eval\\
		\newline
		\vspace{0.01pt}\hfill{}qualitative eval {\qipa ↗}\\
		\columnbreak
		\begin{tabular}{lr}
			\toprule
			error type & count \\
			\midrule
			Missing stem & 364 \\
			Other & 65 \\
			Morphotactics & 19 \\
			Phonology & 8 \\
			Categorisation & 6 \\
			\bottomrule
		\end{tabular}
		\end{multicols}
		%\vspace{0.05em}

@@

		\headerbox{Ongoing and future work}{name=nedostatki,column=1,below=example}{
		\htwo{our other Turkic-language transducers}
		\begin{itemize}
			%\item Turkish (\hiliteone{Çöltekin, 2010 \& 2014}; \hilitetwo{Oflazer, 1994})
			%\item Crimean Tatar (\hilitetwo{Altıntaş, 2001})
			%\item Turkmen (\hilitetwo{Tantuğ et al., 2006})
			%\item Kazakh (\hilitetwo{Бекманова \& Махимов, 2013})
			%\vspace{1pt}\hfill{} \hiliteone{GPL (=free and open)}!
			%\item our Kyrgyz, Kazakh, Tatar, Kumyk:\ all \hiliteone{GPL (=free and open)}!
			\item \textbf{Kyrgyz} \parencite{jnwmifmt2012lrecpaper}%  (Washington et al., 2012)
			\item \textbf{Tatar} \& \textbf{Bashkort} \parencite{fmtjnwisrb2012lrecpaper} %(Tyers et al., 2012)
			\item \textbf{Kazakh} \parencite{isjnwfmt2013mtsummitpaper} %(Salimzyanov et al., 2013)
			\item \textbf{Kumyk} \parencite{jnwisfmt2014lrecpaper} %(Washington et al., 2014)
			\item ongoing work on Sakha, Khakas, and more!
		\end{itemize}
		\dividerspace{}

@@

	\headerbox{References}{name=references,below=results,column=2}{
		\vspace{-0.42em}
		\begin{spacing}{0.3}
			\printbibliography[heading=none]
		\end{spacing}
		\vspace{-0.05em}
	}
